CudeleFS: Programmable Consistency and Durability\\in a Global Namespace

### 2017-04-01 paper/sections/0_abstract.tex
Fixes typos and minor grammar edits

HPC developers are abandoning POSIX because the synchronization and
serialization overheads of providing strong consistency and durability are too
costly -- and often uneccessary -- for their applications.  Unfortunately,
designing near-POSIX file systems excludes applications that rely on strong
consistency or durability, forcing developers to re-write their applications or
deploy them on a different system.  We present a file system and API that
lets clients to specify their consistency/durability requirements and assign
them to subtrees in the namespace, allowing administrators to optimize subtrees
within the same namespace for different workloads.  We draw conclusions about
the performance impact of unexplored consistency/durability metadata designs
and show that strong consistency can cause a 104\(\times\) slow down while merging
updates (7\(\times\) slow down) and maintaining durability (\(10\times\) slow
down) have more reasonable costs.

>>>>

HPC developers are abandoning POSIX because the synchronization and
serialization overheads of providing strong consistency and durability are too
costly -- and often uneccessary -- for their applications.  Unfortunately,
designing near-POSIX file systems excludes applications that rely on strong
consistency or durability, forcing developers to re-write their applications or
deploy them on a different system.  We present a file system and API that
lets clients specify their consistency/durability requirements and assign
them to subtrees in the namespace, allowing users to optimize subtrees
within the same namespace for different workloads.  We draw conclusions about
the performance impact of unexplored consistency/durability metadata designs
and show that strong consistency can cause a 104\(\times\) slow down while merging
updates (7\(\times\) slow down) and maintaining durability (\(10\times\) slow
down) have more reasonable costs.

### 2017-04-01 paper/sections/1_introduction.tex
Fixes typos and minor grammar edits

% What is HPC doing?
To address this, developers are relaxing the consistency and durability
semantics in the file system because weaker guarantees are sufficient for their
applications. For example, batch style jobs often do not need the strong
consistency that the file system provides, so
BatchFS~\cite{zheng:pdsw2014-batchfs} and DeltaFS~\cite{zheng:pdsw2015-deltafs}
do more client side processing and merge updates when the job is done. HPC
developers are turning to this non-POSIX solution because their applications
are well-understood ({\it e.g.}, well-defined read/write phases,
synchronization only needed during certain phases, workflows describing
computation, etc.) and because they wreak havoc on file systems designed for
general-purpose workloads ({\it e.g.}, checkpoint-restart's N-N and N-1 create
patterns).

% One example
One popular approach for relaxing consistency and durability is to ``decouple
the namespace", where clients lock the subtree they want exclusive access to as
a way to tell the file system that the subtree is important or may cause
resource contention in the near-future~\cite{grider:pdsw2015-marfs,
zheng:pdsw2015-deltafs, zheng:pdsw2014-batchfs, ren:sc2014-indexfs,
bent:slides-twotiers}. Then the file system can change its internal structure
to optimize performance. For example, the file system could enter a mode that
prevents other clients from interferring with the decoupled directory.  This
delayed merge ({\it i.e.} a form of eventual consistency) and relaxed
durability improves performance and scalability by avoiding the costs of RPCs,
synchronization, false sharing, and serialization.  The consistency and
durability semantics for these systems is shown in the table in
Figure~\ref{fig:subtree-policies} . While the performance benefits are obvious
for these users, applications that rely on the file system's guarantees must be
deployed on an entirely different system or re-written to coordinate strong
consistency/durability themselves.

@@

% What did we do
We propose subtree policies, an interface that lets future programmers control
the consistency and durability for subtrees in the file system namespace. For performance, one
subtree can adopt weaker consistency semantics while another subtree can retain
the rigidity of POSIX's strong consistency. Figure~\ref{fig:subtree-policies}
shows an example setup where a single global namespace has directories for
applications designed for different, state-of-the-art HPC architectures.  We
present Cudele, a prototype programmable file system that supports different
degrees of consistency and durability by exposing mechanisms used within the
file system as a client library.  Cudele supports 3 forms of consistency
(invisible, weak, and strong) and 3 degrees of durability (none, local, and
global) giving the administrator a wide range of policies and optimizations
that can be custom fit to an application. Our contributions:

@@

  \item a comparison of the strategies used in recently proposed research systems against
  previously unexplored metadata designs.

@@

% Results
Our results confirm the assertions of ``clean-state" research systems that
decouple namespaces; specifically that the technique drastically improve
performance (104\(\times\) speed up) but we go a step further by quantifying
the costs of merging updates (7\(\times\) slow down) and maintaining durability
(\(10\times\) slow down). We also show the effect of having a metadata specific
file format in systems that are based on in-memory data structures.
Section~\ref{sec:related-work} places Cudele in the context of other related
work. Section~\ref{sec:posix-overheads} quantifies the cost of POSIX
consistency and system-defined durability and
Section~\ref{sec:methodology-decoupled-namespaces} presents the Cudele
prototype and API. Section~\ref{sec:implementation} describes Cudele's
mechanisms and shows how re-using internal subsystems results in an
implementation of less than 500 lines of code. The evaluation in
Section~\ref{sec:evaluation} quantifies the overheads and performance gains of
explored and previously unexplored metadata designs.

>>>>

% What is HPC doing?
To address this, developers are relaxing the consistency and durability
semantics in the file system because weaker guarantees are sufficient for their
applications. For example, batch style jobs often do not need the strong
consistency that the file system provides, so
BatchFS~\cite{zheng:pdsw2014-batchfs} and DeltaFS~\cite{zheng:pdsw2015-deltafs}
do more client-side processing and merge updates when the job is done. HPC
developers are turning to these non-POSIX solutions because their applications
are well-understood ({\it e.g.}, well-defined read/write phases,
synchronization only needed during certain phases, workflows describing
computation, etc.) and because they wreak havoc on file systems designed for
general-purpose workloads ({\it e.g.}, checkpoint-restart's N-N and N-1 create
patterns).

% One example
One popular approach for relaxing consistency and durability is to ``decouple
the namespace", where clients lock the subtree they want exclusive access to as
a way to tell the file system that the subtree is important or may cause
resource contention in the near-future~\cite{grider:pdsw2015-marfs,
zheng:pdsw2015-deltafs, zheng:pdsw2014-batchfs, ren:sc2014-indexfs,
bent:slides-twotiers}. Then the file system can change its internal structure
to optimize performance. For example, the file system could enter a mode that
prevents other clients from interferring with the decoupled directory.  This
delayed merge ({\it i.e.} a form of eventual consistency) and relaxed
durability improves performance and scalability by avoiding the costs of RPCs,
synchronization, false sharing, and serialization.  The consistency and
durability semantics for these systems is shown in
Figure~\ref{fig:subtree-policies} (table) . While the performance benefits are obvious
for these users, applications that rely on the file system's guarantees must be
deployed on an entirely different system or re-written to coordinate strong
consistency/durability themselves.

@@

% What did we do
We propose a subtree policy API that lets future programmers control
the consistency and durability for subtrees in the file system namespace. For performance, one
subtree can adopt weaker consistency semantics while another subtree can retain
the rigidity of POSIX's strong consistency. Figure~\ref{fig:subtree-policies}
shows an example setup where a single global namespace has directories for
applications designed for different, state-of-the-art HPC architectures.  We
present Cudele, a prototype programmable file system that supports different
degrees of consistency and durability by exposing mechanisms used within the
file system as a client library.  Cudele supports 3 forms of consistency
(invisible, weak, and strong) and 3 degrees of durability (none, local, and
global) giving the administrator a wide range of policies and optimizations
that can be custom fit to an application. Our contributions:

@@

  \item an apples-to-apples comparison of the strategies used in recently proposed research systems against
  previously unexplored metadata designs, all implemented using Cudele.

@@

% Results
Our results confirm the assertions of ``clean-state" research systems that
decouple namespaces; specifically that the technique drastically improves
performance (104\(\times\) speed up) but we go a step further by quantifying
the costs of merging updates (7\(\times\) slow down) and maintaining durability
(\(10\times\) slow down). We also show the effect of having a metadata specific
file format in systems that are based on in-memory data structures.
Section~\ref{sec:posix-overheads} quantifies the cost of POSIX
consistency and system-defined durability and
Section~\ref{sec:methodology-decoupled-namespaces} presents the Cudele
prototype and API. Section~\ref{sec:implementation} describes Cudele's
mechanisms and shows how re-using internal subsystems results in an
implementation of less than 500 lines of code. The evaluation in
Section~\ref{sec:evaluation} quantifies the overheads and performance gains of
explored and previously unexplored metadata designs.
Section~\ref{sec:related-work} places Cudele in the context of other related
work.

### 2017-04-01 paper/sections/2_related_work.tex
Fixes typos and minor grammar edits

% approaches to load balancing (strong = more resuorces per unit work, weak =
% fixed resource per work unit)
One approach for improving metadata performance and scalability is to alleviate
overloaded servers by load balancing metadata IO across a cluster. Common
techniques include partitioning metadata when there are many writes and
replicating metadata when there are many reads. For example, IndexFS~\cite{ren:sc2014-indexfs} partitions
directories and clients write to different partitions by grabbing leases and
caching ancestor metadata for path traversal; it does well for strong scaling
because servers can keep more inodes in the cache which results in less RPCs.
Alternatively, ShardFS replicates directory state so servers do not need to
contact peers for path traversal; it does well for read workloads because all
file operations only require 1 RPC and for weak scaling because requests will
never incurr extra RPCs due to a full cache.  CephFS employs both techniques to
a lesser extent; directories can be replicated or sharded but the caching and
replication policies do not change depending on the balancing technique.
Despite the performance benefits these techniques add complexity and jeopardize
the robustness and performance characteristics of the metadata service because
the systems now need (1) policies to guide the migration decisions and (2)
mechanisms to address inconsistent states across servers.

@@

% addressing inconsistency
In addition to the policies, distributing metadata across a cluster requiress
distributed transactions and cache coherence protocols to ensure strong
consistency ({e.g.}, POSIX).  For example, ShardFS pessimistically replicates
directory state and uses optimistic concurrency control for conflicts; namely
it does the operation and if there is a conflict at verification time it falls
back to two-phase locking.  Another example is IndexFS's inode cache which
reduces RPCs by caching ancestor paths -- the locality of this cache can be
thrashed by random reads but performs well for metadata writes. For
consistency, writes to directories in IndexFS block until the lease expires
while writes to directories in ShardFS are slow for everyone as it either
requires serialization or locking with many servers; reads in IndexFS are
subject to cache locality while reads in ShardFS always resolve to 1 RPC.
Another example of the overheads of addressing inconsistency is how CephFS
maintains client sessions and inode caches for capabilities (which in turn make
metadata access faster). When metadata is exchanged between metadata servers
these sessions/caches must be flushed and new statistics exchanged with a
scatter-gather process; this halts updates on the directories and blocks until
the authoratitive metadata server responds.  These protocols are discusssed in
more detail in the next section but their inclusion here is a testament to the
complexity of migrating metadata.

@@

% Non POSIX
High performance computing has unique requirements for file systems ({\it
e.g.}, fast creates) and well-defined workloads ({\it e.g.}, workflows) that
make relaxing POSIX sensible.  BatchFS assumes the application coordinates
accesses to the namespace, so the clients can batch local operations and merge
with a global namespace image lazily. Similarily, DeltaFS eliminates RPC
traffic using subtree snapshots for non-conflicting workloads and middleware
for conflicting workloads. MarFS gives administrators the ability to lock
``project directories" and allocate GPFS clusters for demanding metadata
workloads. TwoTiers eliminates high-latencies by storing metadata in a flash
tier; apps lock the namespace so that metadata can be accessed more quickly.
Unfortunately, decoupling the namespace has costs: (1) merging metadata state
back into the global namespace is slow; (2) failures are local to the failing
node; and (3) the systems are not backwards compatible.

@@

For (1), state-of-the-art systems manage consistency in non-traditional ways:
IndexFS maintains the global namespace but blocks operations from other clients
until the first client drops the lease, BatchFS does operations on a snapshot
of the namespace and merges batches of operations into the global namespace,
and DeltaFS never merges back into the global namespace. The merging for
BatchFS is done by an auxiliary metadata server running on the client and
conflicts are resolved by the application. Although DeltaFS never explicitly
merges, applications needing some degree of ground truth can either manage
consistency thesmelves on a read or add a bolt-on service to manage the
consistency.

>>>>

% approaches to load balancing (strong = more resuorces per unit work, weak =
% fixed resource per work unit)
One approach for improving metadata performance and scalability is to alleviate
overloaded servers by load balancing metadata IO across a cluster. Common
techniques include partitioning metadata when there are many writes and
replicating metadata when there are many reads. For example, IndexFS~\cite{ren:sc2014-indexfs} partitions
directories and clients write to different partitions by grabbing leases and
caching ancestor metadata for path traversal; it does well for strong scaling
because servers can keep more inodes in the cache which results in less RPCs.
Alternatively, ShardFS replicates directory state so servers do not need to
contact peers for path traversal; it does well for read workloads because all
file operations only require 1 RPC and for weak scaling because requests will
never incur extra RPCs due to a full cache.  CephFS employs both techniques to
a lesser extent; directories can be replicated or sharded but the caching and
replication policies do not change depending on the balancing technique.
Despite the performance benefits these techniques add complexity and jeopardize
the robustness and performance characteristics of the metadata service because
the systems now need (1) policies to guide the migration decisions and (2)
mechanisms to address inconsistent states across servers.

@@

% addressing inconsistency
In addition to the policies, distributing metadata across a cluster requiress
distributed transactions and cache coherence protocols to ensure strong
consistency ({e.g.}, POSIX).  For example, ShardFS pessimistically replicates
directory state and uses optimistic concurrency control for conflicts; namely
it does the operation and if there is a conflict at verification time it falls
back to two-phase locking.  Another example is IndexFS's inode cache which
reduces RPCs by caching ancestor paths -- the locality of this cache can be
thrashed by random reads but performs well for metadata writes. For
consistency, writes to directories in IndexFS block until the lease expires
while writes to directories in ShardFS are slow for everyone as it either
requires serialization or locking with many servers; reads in IndexFS are
subject to cache locality while reads in ShardFS always resolve to 1 RPC.
Another example of the overheads of addressing inconsistency is how CephFS
maintains client sessions and inode caches for capabilities (which in turn make
metadata access faster). When metadata is exchanged between metadata servers
these sessions/caches must be flushed and new statistics exchanged with a
scatter-gather process; this halts updates on the directories and blocks until
the authoritative metadata server responds.  These protocols are discussed in
more detail in the next section but their inclusion here is a testament to the
complexity of migrating metadata.

@@

% Non POSIX
High performance computing has unique requirements for file systems ({\it
e.g.}, fast creates) and well-defined workloads ({\it e.g.}, workflows) that
make relaxing POSIX sensible.  BatchFS assumes the application coordinates
accesses to the namespace, so the clients can batch local operations and merge
with a global namespace image lazily. Similarly, DeltaFS eliminates RPC
traffic using subtree snapshots for non-conflicting workloads and middleware
for conflicting workloads. MarFS gives administrators the ability to lock
``project directories" and allocate GPFS clusters for demanding metadata
workloads. TwoTiers eliminates high-latencies by storing metadata in a flash
tier; apps lock the namespace so that metadata can be accessed more quickly.
Unfortunately, decoupling the namespace has costs: (1) merging metadata state
back into the global namespace is slow; (2) failures are local to the failing
node; and (3) the systems are not backwards compatible.

@@

For (1), state-of-the-art systems manage consistency in non-traditional ways:
IndexFS maintains the global namespace but blocks operations from other clients
until the first client drops the lease, BatchFS does operations on a snapshot
of the namespace and merges batches of operations into the global namespace,
and DeltaFS never merges back into the global namespace. The merging for
BatchFS is done by an auxiliary metadata server running on the client and
conflicts are resolved by the application. Although DeltaFS never explicitly
merges, applications needing some degree of ground truth can either manage
consistency themselves on a read or add a bolt-on service to manage the
consistency.

### 2017-04-01 paper/sections/3_posix_overheads.tex
Uses times as main font
Fixes typos and minor grammar edits

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{Create-heavy workloads (untar) incurr the highest disk, network, and
CPU utilization because of the consistency and durability demands of
CephFS.}\label{fig:overhead-creates}
\end{figure}

In our examiniation of the overheads of POSIX we benchmark and analyze CephFS,
the file system that uses the Ceph's object store ({\it i.e.} RADOS) to store
its data and metadata. We choose CephFS because it is an open-source production
quality system. This file system is an implementation of one set of design
decisions and our goal is to highlight the effect that those decisions have on
performance.

To show how the file system behaves under high metadata load we use a
create-heavy workload. Create-heavy workloads are studied the most in HPC
research because of the checkpoint/restart use case but they also happen to
stress the underyling storage system the most.
Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The untar phase, which is characterized by many creates, has
the highest resource usage which suggests that it is stressing the consistency
and journaling subsystems of the metadata server the most. Traditional file
system techniques for improving performance, such as caching inodes, do not
help for create-heavy workloads.

In this section, we quantify the costs of strong consistency and global
durability in CephFS. At the end of each subsection we compare the approach to
``decoupled namespaces", the technique in related work that detaches subtrees
from the global namespace to relax consistency/durability guarantees.  We use
the kernel client so that we can find the true create speed of the server; our
experiments show a low CPU utilziation for the clients which indicates that we
are stressing the servers more.

@@

% - sequential IO, trim redundant operations
\noindent\textbf{CephFS Design}: a journal of metadata updates that streams into
the resilient object store. Similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL} the metadata journal is designed to grow to large which
ensures (1) sequential writes into the object store and (2) the ability for daemons to
trim redundant or irrelevent journal entries.  The journal is striped over
objects where multiple journal updates can reside on the same object. There are
two tunables for controlling the journal: the segment size and the number of
parallel segments that can be written in parallel. Unless the journal saturates 
memory or CPU resources, larger values for these tunables results in better
performance.

% purpose of the journal
As shown in Figure~\ref{fig:journal}, in addition to the metadata journal,
CephFS also represents metadata in RADOS as a metadata store, where directories
and their file inodes are stored as objects.  The metadata server applies the
updates in the journal to the metadata store when the journal reaches a certain
size. The metadata store is optimized for recovery ({\it i.e.} reading) while
the metadata journal is write-optimized.

% Effects on performance
Figure~\ref{fig:slowdown-journal} shows that journaling metadata updates into
the object store has an overhead. Figure~\ref{fig:slowdown-journal-a} shows the
effect of journaling of different journal segment sizes; the larger the segment
size the bigger that the writes into the object store are. The trade-off for
better performance is memory consumption because larger segment sizes take up
more space with their buffers. Figure~\ref{fig:slowdown-journal-b} shows how
the metadata server periodically stops serving requests to flush ({\it i.e.}
apply journal updates to) the metadata store.  The journal overhead is
sufficient enough to slow down metadata throughput but not so much as to
overwhelm the bandidth of the object store. We measured our peak bandwidth to
be 100MB/s, which is the speed of our network link.\\

\noindent\textbf{Comparison to decoupled namespaces}: In BatchFS and DeltaFS,
as far as we can tell, when a client or server fails there is no recovery
scheme. For BatchFS, if a client fails when it is writing to the local
log-structured merged tree (implemented as an SSTable) then those batched
metadata operations are lost. For DeltaFS, if the client fails then on restart
the computation does the work again -- since the snapshots of the namespace are
never globally consistent and there is no ground truth.  On the server side,
BatchFS and DeltaFS use IndexFS. IndexFS writes metadata to SSTables, which
initially reside in memory but are later to flushed to the underlying
distributed file system.

@@

\noindent\textbf{CephFS Design}: capabilities keep metadata strongly
consistent. To reduce the number of RPCs needed for consistency, clients can
obtain capabilities for reading, reading and updating, caching reads, writing,
buffering writes, changing the file size, and performing lazy IO.

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/behavior-interfere.png}
      \caption{Inteference forces \texttt{lookup()}s}
      \label{fig:interfere-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere.png}
      \caption{Interference hurts performance}
      \label{fig:interfere-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere-types.png}
      \caption{Different interferring requests}
      \label{fig:interfere-c}
  \end{subfigure}
  \caption{When a client create stream is ``isolated" then lookups resolve
  locally but when a second client ``interferes" by creating in the same
  directory, the directory inode capability is revoked forcing all clients to
  centralize lookups at the metadata server.  
  \label{fig:interfere}}
\end{figure*}

@@

% benefits PROBLEM -- IS THIS THE METADATA PROTOCOL OR JUST THE OVERLOADEDNESS?
The benefits of caching the directory inode when creating files is shown in
Figure~\ref{fig:interfere-a}.  If only one client is creating files in a
directory (``isolated" curve on \(y1\) axis) then that client can lookup the
existence of new files locally before issuing a create request to the metadata
server. If another client starts creating files in the same directory
(``interfere" curve on \(y1\) axis) then the directory inode transitions out of
read caching and the first client must send \texttt{lookup()}s to the metadata
server (``interfere" curve on \(y2\) axis). These extra requests increase the
throughput of the ``interfere" curve because the metadata server can handle the
extra load but the overall performance decreases.  This degradation is shown in
Figure~\ref{fig:interfere-b}, where we scale the number of clients and show
increased runtime and variability. The performance is compared to a single
isolated client and the error bar is the standard deviation of the runtime of
all clients.  For the ``interfere" bars, each client creates files in private
directories and at 30 seconds we launch another process that creates files in
those directories.  For less than 7 clients, the runtime and deviation is worse
when clients interfere. At 7 clients, the metadata server is overloaded so the
directory caching in the ``isolated" bars has no benefit. Zooming in on runs
with 7 clients in Figure~\ref{fig:interfere-c} we see how different
interferring operations affect performance, again when compared to the
performance of a single isolate client.  ``create" has little effect but
``stat" and ``create many" cause noticeable slowdowns because of the extra work
they impose on the metadata server.\\

@@

\noindent\textbf{Comparison to decoupled namespaces}: Decoupled namespaces
merge batches of metadata operations into the global namespaces when the job
completes.  In BatchFS the merge is delayed by the application using an API to
switch between asynchronous to sychronous mode. The merge itself is explicitly
managed by the application but future work looks at more automated
methdologies. In DeltaFS snapshots of the metadata subtrees stays on the client
machines; there is no ground truth and consistent namespaces are constructed
and resolved at application read time or when a 3rd party system ({\it e.g.},
middleware, scheduler, etc.) needs a view of the metadata. As a result, all the
overheads of maintaining consistency that we showed above are delayed until the
merge phase.

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{Create-heavy workloads (such as \texttt{untar}) incur the highest disk, network, and
CPU utilization because of the consistency and durability demands of
CephFS.}\label{fig:overhead-creates}
\end{figure}

In our examination of the overheads of POSIX we benchmark and analyze CephFS,
the file system that uses the Ceph's object store ({\it i.e.} RADOS) to store
its data and metadata. We choose CephFS because it is an open-source production
quality system. This file system is an implementation of one set of design
decisions and our goal is to highlight the effect that those decisions have on
performance.

To show how the file system behaves under high metadata load we use a
create-heavy workload. Create-heavy workloads are studied the most in HPC
research because of the checkpoint/restart use case but they also happen to
stress the underlying storage system the most.
Figure~\ref{fig:overhead-creates} shows the resource utilization of compiling
the Linux kernel.  The \texttt{untar} phase, which is characterized by many creates, has
the highest resource usage which suggests that it is stressing the consistency
and journaling subsystems of the metadata server the most. Traditional file
system techniques for improving performance, such as caching inodes, do not
help for create-heavy workloads.

In this section, we quantify the costs of strong consistency and global
durability in CephFS. At the end of each subsection we compare the approach to
``decoupled namespaces", the technique in related work that detaches subtrees
from the global namespace to relax consistency/durability guarantees.  We use
the kernel client so that we can find the true create speed of the server; our
experiments show a low CPU utilization for the clients which indicates that we
are stressing the servers more.

@@

% - sequential IO, trim redundant operations
\noindent\textbf{CephFS Design}: a journal of metadata updates that streams into
the resilient object store, similar to LFS~\cite{rosenblum:acm1992-LFS} and
WAFL~\cite{hitz:wtec1994-WAFL}, grows to large extents which
allows to (1) sequentially write into the object store and (2) provide the ability for daemons to
trim redundant or irrelevant journal entries.  The journal is striped over
objects where multiple journal updates can reside on the same object. There are
two tunables for controlling the journal: the segment size and the number of
parallel segments that can be written in parallel. Unless the journal saturates 
memory or CPU resources, larger values for these tunables results in better
performance.

% purpose of the journal
As shown in Figure~\ref{fig:journal}, in addition to the metadata journal,
CephFS also stores metadata in RADOS, where directories
and their file inodes are stored as objects.  The metadata server applies the
updates in the journal to this metadata store when the journal reaches a certain
size. The metadata store is optimized for recovery ({\it i.e.} reading) while
the metadata journal is write-optimized.

% Effects on performance
Figure~\ref{fig:slowdown-journal} shows that journaling metadata updates into
the object store has an overhead. Figure~\ref{fig:slowdown-journal-a} shows the
effect of journaling of different journal segment sizes; the larger the segment
size the bigger that the writes into the object store are. The trade-off for
better performance is memory consumption because larger segments take up
more space for buffering. Figure~\ref{fig:slowdown-journal-b} shows how
the metadata server periodically stops serving requests to flush ({\it i.e.}
apply journal updates to) to the metadata store.  The journal overhead is
sufficient enough to slow down metadata throughput but not so much as to
overwhelm the bandwidth of the object store. We measured our peak bandwidth to
be 100MB/s, which is the speed of our network link.\\

\noindent\textbf{Comparison to decoupled namespaces}: In BatchFS and DeltaFS,
to the best of our knowledge, when a client or server fails there is no recovery
scheme. For BatchFS, if a client fails when it is writing to the local
log-structured merged tree (implemented as an SSTable) then those batched
metadata operations are lost. For DeltaFS, if the client fails then, on restart,
the computation does the work again -- since the snapshots of the namespace are
never globally consistent and there is no ground truth.  On the server side,
BatchFS and DeltaFS use IndexFS. IndexFS writes metadata to SSTables, which
initially reside in memory but are later flushed to the underlying
distributed file system.

@@

\noindent\textbf{CephFS Design}: capabilities keep metadata strongly
consistent. To reduce the number of RPCs needed for consistency, clients can
obtain capabilities for reading, creating and updating inodes, as well as caching reads,
buffering writes, changing the file size, and performing lazy IO.

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/behavior-interfere.png}
      \caption{Inteference forces \texttt{lookup()}s}
      \label{fig:interfere-a}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere.png}
      \caption{Interference hurts performance}
      \label{fig:interfere-b}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere-types.png}
      \caption{Different interferring requests}
      \label{fig:interfere-c}
  \end{subfigure}
  \caption{When a client create stream is ``isolated" lookups resolve
  locally; but when a second client ``interferes" by creating in the same
  directory, the directory inode capability is revoked forcing all clients to
  centralize lookups at the metadata server.
  \label{fig:interfere}}
\end{figure*}

@@

% benefits PROBLEM -- IS THIS THE METADATA PROTOCOL OR JUST THE OVERLOADEDNESS?
The benefits of caching the directory inode when creating files is shown in
Figure~\ref{fig:interfere-a}.  If only one client is creating files in a
directory (``isolated" curve on \(y1\) axis) then that client can lookup the
existence of new files locally before issuing a create request to the metadata
server. If another client starts creating files in the same directory
(``interfere" curve on \(y1\) axis) then the directory inode transitions out of
read caching and the first client must send \texttt{lookup()}s to the metadata
server (``interfere" curve on \(y2\) axis). These extra requests increase the
throughput of the ``interfere" curve because the metadata server can handle the
extra load but the overall performance decreases.  This degradation is shown in
Figure~\ref{fig:interfere-b}, where we scale the number of clients and show
increased runtime and variability. The performance is compared to a single
isolated client and the error bar is the standard deviation of the runtime of
all clients.  For the ``interfere" bars, each client creates files in private
directories and at 30 seconds we launch another process that creates files in
those directories.  For less than 7 clients, the runtime and deviation is worse
when clients interfere. At 7 clients, the metadata server is overloaded so the
directory caching in the ``isolated" bars has no benefit. Zooming in on runs
with 7 clients in Figure~\ref{fig:interfere-c} we see how different
interfering operations affect performance, again when compared to the
performance of a single isolate client.  ``create" has little effect but
``stat" and ``create many" cause noticeable slowdowns because of the extra work
they impose on the metadata server.\\

@@

\noindent\textbf{Comparison to decoupled namespaces}: Decoupled namespaces
merge batches of metadata operations into the global namespaces when the job
completes.  In BatchFS the merge is delayed by the application using an API to
switch between asynchronous to synchronous mode. The merge itself is explicitly
managed by the application but future work looks at more automated
methodologies. In DeltaFS snapshots of the metadata subtrees stays on the client
machines; there is no ground truth and consistent namespaces are constructed
and resolved at application read time or when a 3rd party system ({\it e.g.},
middleware, scheduler, etc.) needs a view of the metadata. As a result, all the
overheads of maintaining consistency that we showed above are delayed until the
merge phase.

### 2017-04-01 paper/sections/4_methodology.tex
Fixes typos and minor grammar edits

% describe table
The spectrum of consistency and durability guarantees that adminstrators can
construct is shown in Table~\ref{table:spectrum}. The columns are the different
consistency semantics and the rows cover the spectrum of durability guarantees.
For consistency: ``invisible" means the system does not handle merging updates
into a global namespace and it is assumed that middleware or the application
manages consistency lazily; ``weak" merges updates at some time in the
future ({\it e.g.}, when the system has time, when number of updates reaches a
certain threshold, when the client is done writing, etc.); and updates in
``strong" consistency are seen immediately by all clients. For durability,
``none" means that updates are volatile and will be lost on a failure. Stronger
guarantees are made with ``local", which means updates will be retained if the
client node recovers, and ``global", where all updates are always recoverable.

@@

% talk of eventual consistency
The consistency and durability properties in Table~\ref{table:spectrum} are not
guaranteed until all mechanisms in the cell are complete. The compositions
should be considered atomic and there are no guarantees while transitioning
between policies. For example, updates are not deemed globally consistent until
they are safely saved in the object store. If a failure occurs during ``global
persist" or if we inject a new policy that chanages a subtree from ``local
persist" to ``global persist", CudeleFS no guarantee until the mechanisms are
complete.

>>>>

% describe table
The spectrum of consistency and durability guarantees that administrators can
construct is shown in Table~\ref{table:spectrum}. The columns are the different
consistency semantics and the rows cover the spectrum of durability guarantees.
For consistency: ``invisible" means the system does not handle merging updates
into a global namespace and it is assumed that middleware or the application
manages consistency lazily; ``weak" merges updates at some time in the
future ({\it e.g.}, when the system has time, when number of updates reaches a
certain threshold, when the client is done writing, etc.); and updates in
``strong" consistency are seen immediately by all clients. For durability,
``none" means that updates are volatile and will be lost on a failure. Stronger
guarantees are made with ``local", which means updates will be retained if the
client node recovers, and ``global", where all updates are always recoverable.

@@

% talk of eventual consistency
The consistency and durability properties in Table~\ref{table:spectrum} are not
guaranteed until all mechanisms in the cell are complete. The compositions
should be considered atomic and there are no guarantees while transitioning
between policies. For example, updates are not deemed globally consistent until
they are safely saved in the object store. If a failure occurs during ``global
persist" or if we inject a new policy that changes a subtree from ``local
persist" to ``global persist", CudeleFS no guarantee until the mechanisms are
complete.

### 2017-04-01 paper/sections/5_implementation.tex
Fixes typos and minor grammar edits

We use a ``programmable storage" approach~\cite{sevilla:eurosys17} to design
CudeleFS; namely, we try to leverage components inside Ceph to inherit the
robustness and correctness of the internal subsystems. In this section, we
first describe a Ceph internal subsystem or component and then we show how we
use it in CudeleFS.

>>>>

We use a programmable storage approach~\cite{sevilla:eurosys17} to design
CudeleFS; namely, we try to leverage components inside Ceph to inherit the
robustness and correctness of the internal subsystems. In this section, we
first describe a Ceph internal subsystem or component and then we show how we
use it in CudeleFS.
